---
title: "simpleRegress"
author: "Dominic Garibay"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 


```{r}
age <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(age)
summary.lm(age)
```

```{r}
width <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(width)
summary.lm(width)
```

```{r}
weight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(weight)
summary.lm(weight)
```


```{r}
chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chest)
summary.lm(chest)
```


```{r}
headlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlen)
summary.lm(headlen)
```

Here is the order from worst to best of the different variables correlated to the length of a bear by their residual standard error and their adjusted R-squared:

1.LENGTH~AGE: Residual standard error: 7.5 on 52 degrees of freedom, Adjusted R-Squared: 0.50 

2.LENGTH~HEADWTH: Residual standard error: 7.32 on 52 degrees of freedom,	Adjusted R-squared:  0.5321

3.LENGTH~WEIGHT: Residual standard error: 5.4 on 52 degrees of freedom, Adjusted R-squared: 0.7

4.LENGTH~NECK: Residual standard error: 5.376 on 52 degrees of freedom,	Adjusted R-squared:  0.7476

5.LENGTH~CHEST:Residual standard error: 4.939 on 52 degrees of freedom
Multiple R-squared:  0.791,	Adjusted R-squared:  0.7869 

6.LENGTH~HEADLEN: Residual standard error: 4.235 on 52 degrees of freedom,	Adjusted R-squared:  0.8434 
